\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}

\usepackage{todonotes}
\usepackage{makecell}
\usepackage{graphicx}
\usepackage{adjustbox}
\usepackage{paralist}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{cleveref}

\modulolinenumbers[5]
\renewcommand\theadalign{rb}
\newcolumntype{R}[1]{>{\tiny\raggedleft\arraybackslash}b{#1}}

% Comment the following for final version
\setlength{\marginparwidth}{4cm} % expand note margin
%%%%%%%%%%%%%%%%%%%%%%%


\journal{Journal of \LaTeX\ Templates}
\bibliographystyle{elsarticle-num}

\newcommand{\trademark}{{\tiny\textsuperscript\textregistered}}

\input{commands}

\begin{document}

\begin{frontmatter}

\title{DEPRECATED. Please follow link in abstract to the correct overleaf project.}

        \author[tug]{G.~Schweiger}
        \author[ant]{C.~Gomes }
        \author[tug]{G.~Engel}
        \author[dwh]{I.~Hafner}
        \author[swe]{J.~Schoeggl}
        \author[kfu]{A. Posch}
        \author[lbnl]{T.~Nouidui \corref{cor1}}

        \address[tug]{Technical University of Graz, Austria}
        \address[ant]{University of Antwerp, Antwerp, Belgium}
        \address[dwh]{dwh GmbH - Simulation Services and Technical Solutions, Vienna, Austria}
        \address[swe]{KTH Royal Institute of Technology, Stockholm, Sweden}
        \address[kfu]{University of Graz, Austria}
        \address[lbnl]{Lawrence Berkeley National Laboratory, Berkeley, USA}


        \cortext[cor1]{Corresponding author. yyy
        000, 000 Berkeley, USA. Tel.: +xxxxxx \textit{E-mail address}: tsnouidui@lbl.gov}

\begin{abstract}

{
\url{https://v2.overleaf.com/5389137161csybdfnnjtmg}
}


\end{abstract}

\begin{keyword}
Co-Simulation \sep Survey \sep Delphi Method
\end{keyword}

\end{frontmatter}

%\linenumbers

\input{chapter/Introduction}

\claudio{I think we need a background section. This is a journal paper: it should be somewhat self contained. A basic requirement is: the readers should be able to understand the questions being asked. I can prepare a draft background section if you want, or we can reuse what we already have from previous papers, and expand it.}

\input{chapter/Method}
\input{chapter/ResultsDiscussion}
\input{chapter/Conclusion}


\section*{Acknowledgement}
We want to thank all experts who participated in the study. 
\section{References}

\bibliography{Literature,Mendeley,mendeley_v2,bib_claudio}

\input{chapter/Appendix}
\newpage
\end{document}
